Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-18 manuscript/climate_sensitivity_draft.Rmd
more emphasis in combined-years model in results (started, not complete)
#113

Taller trees showed stronger growth reductions during drought when evaluating the three drought years together and for 1966 individually (Table 1; Fig. **4**). 
Specifically, $ln[H]$ appeared, with negative coefficient, in the best models and all top models (Tables S6-S7).
For the 1977 drought, $ln[H]$ did not appear in the best model, but was included, with negative coefficient, among the top models--*i.e.*, models that were statistically indistinguishable ($\Delta$AICc<2) from the best model (Tables 1, S6-S7). 
For the 1999 drought, $ln[H]$ appeared in no top models for $Rt$ and some top models, with positive coefficient, for $Rt_{ARIMA}$.

>>>>

Taller trees showed stronger growth reductions during drought (Table 1; Fig. **4**). 
Specifically, $ln[H]$ appeared, with negative coefficient, in the best model and all top models when evaluating the three drought years together (Tables S6-S7). 
The same held true for 1966 individually.
For the 1977 drought, $ln[H]$ did not appear in the best model, but was included, with negative coefficient, among the top models--*i.e.*, models that were statistically indistinguishable ($\Delta$AICc<2) from the best model (Tables 1, S6-S7). 
For the 1999 drought, $ln[H]$ had no signficant effect.
